Forecasting interrupted time series

### 2023-07-27 fits.qmd
Still working on tourism

---
title: "Forecasting interrupted time series"
author:
- familyname: Rostami-Tabar
  othernames: Bahman
  address:
    - Cardiff Business School
    - Wales CF10 3EU
    - United Kingdom
  email: rostami-tabarb@cardiff.ac.uk
  correspondingauthor: true
- familyname: Hyndman
  othernames: Rob J
  address:
    - Department of Econometrics & Business Statistics
    - Clayton VIC 3800
    - Australia
  email: Rob.Hyndman@monash.edu
abstract: "A brief summary of our ideas"
keywords: "blah, blah"
wpnumber: no/yr
jelcodes: C10,C14,C22
blind: false
cover: false
toc: false
bibliography: references.bib
biblio-style: authoryear-comp
format: wp-pdf
fig-height: 5
fig-width: 8
keep-tex: true
number-sections: true
cite-method: biblatex
execute:
  echo: false
  warning: false
  message: false
  cache: false
---

@@

```{r}
#| label: fig-tourism_plot1
#| caption: Australian tourism data"
tar_read(tourism_plot1)
```

@@

```{r}
#| label: fig-tsol1_plot
#| fig-height: 8
tar_read(tsol1_plot)
```

```{r}
#| label: fig-tsol3_plot
#| fig-height: 8
tar_read(tsol3_plot)
```

>>>>

---
title: "Forecasting interrupted time series"
author:
- familyname: Rostami-Tabar
  othernames: Bahman
  address:
    - Cardiff Business School
    - Wales CF10 3EU
    - United Kingdom
  email: rostami-tabarb@cardiff.ac.uk
  correspondingauthor: true
- familyname: Hyndman
  othernames: Rob J
  address:
    - Department of Econometrics & Business Statistics
    - Clayton VIC 3800
    - Australia
  email: Rob.Hyndman@monash.edu
abstract: "A brief summary of our ideas"
keywords: "blah, blah"
wpnumber: no/yr
jelcodes: C10,C14,C22
blind: false
cover: false
toc: false
bibliography: references.bib
biblio-style: authoryear-comp
format: 
  wp-pdf:
    include-in-header: header.tex
cite-method: biblatex
number-sections: true
keep-tex: true
fig-height: 5
fig-width: 8
execute:
  echo: false
  warning: false
  message: false
  cache: false
---

@@

```{r}
#| label: fig-tourism_plot1
#| caption: Australian tourism data"
#| fig-height: 3
tar_read(tourism_plot1)
```

@@

```{r}
#| label: fig-tsol1_plot
#| fig-height: 8
#| fig-caption: Solution 1. ETS is highly adaptive.
tar_read(tsol1_plot)
```

```{r}
#| label: fig-tsol2_plot
#| fig-height: 8
#| fig-caption: Solution 2. We use a left shift in March 2020, and a ramp from November 2022.
tar_read(tsol2_plot)
```

```{r}
#| label: fig-tsol3_plot
#| fig-height: 8
#| fig-caption: Solution 3. The period from March 2020 to November 2022 is set to missing.
tar_read(tsol3_plot)
```

```{r}
#| label: fig-tsol4_plot
#| fig-height: 8
#| fig-caption: Solution 4. The period from March 2020 to November 2022 is set to missing.
tar_read(tsol4_plot)
```

\FloatBarrier

### 2023-07-27 fits.tex
Still working on tourism

\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, breakable, interior hidden, enhanced, sharp corners, frame hidden]}{\end{tcolorbox}}\fi
\makeatother
\makeatletter
\makeatother

@@

Advantages: effectively ignores the change period

Disadvantages: throws away the covid-period data, and so starts the
post-covid period with no recent history. Therefore prediction intervals
will be relatively large.

@@

@@

\includegraphics{fits_files/figure-pdf/unnamed-chunk-3-1.pdf}

>>>>

\usepackage[section]{placeins}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, interior hidden, sharp corners, frame hidden, enhanced]}{\end{tcolorbox}}\fi
\makeatother
\makeatletter
\makeatother

@@

Many time series models will handle periods of missing values. So the
problematic observations that occur during the period of disruption can
be set to missing, and the model should continue to produce forecasts as
if the interruption had not occurred. Of course, the forecasts will not
be accurate for the period of disruption, but they can be interpreted as
``what might have been''. This solution requires a judgement to be made
about when the disruption has begun, and when normality resumes.

Because no information is retained during the disruption, the prediction
intervals will become large during the disruption, and after the
disruption they will remain large until the model has enough data to
estimate the forecast distribution more accurately.

@@

The Australian tourism data set is a monthly time series showing the
number of short-term overseas visitors to Australia. The data are
available from January 2000 to May 2023, and are shown in
Figure~\ref{fig-tourism_plot1}. As the borders closed in March 2020, the
number of visitors to Australia dropped to near zero, and remained there
until towards the end of 2021. The borders officially reopened on 21
February 2022, although it seems visitors began to arrive earlier than
that. The data are available from the Australian Bureau of Statistics.

\begin{figure}

{\centering \includegraphics{fits_files/figure-pdf/fig-tourism_plot1-1.pdf}

}

\caption{\label{fig-tourism_plot1}\textbf{?(caption)}}

\end{figure}

We will apply each of the approaches above to this data set, and compare
their performance.

\begin{figure}

{\centering \includegraphics{fits_files/figure-pdf/fig-tsol1_plot-1.pdf}

}

\caption{\label{fig-tsol1_plot}\textbf{?(caption)}}

\end{figure}

\begin{figure}

{\centering \includegraphics{fits_files/figure-pdf/fig-tsol2_plot-1.pdf}

}

\caption{\label{fig-tsol2_plot}\textbf{?(caption)}}

\end{figure}

\begin{figure}

{\centering \includegraphics{fits_files/figure-pdf/fig-tsol3_plot-1.pdf}

}

\caption{\label{fig-tsol3_plot}\textbf{?(caption)}}

\end{figure}

\begin{figure}

{\centering \includegraphics{fits_files/figure-pdf/fig-tsol4_plot-1.pdf}

}

\caption{\label{fig-tsol4_plot}\textbf{?(caption)}}

\end{figure}

\FloatBarrier

@@

\includegraphics{fits_files/figure-pdf/unnamed-chunk-8-1.pdf}
